Figure 1d

### 2017-11-20 inst/3_prime_race/3_prime_race.Rmd
adding 3 primer race schematic

>>>>

```{r, fig.align='center', fig.height=2, fig.width=12, warning = FALSE, message = FALSE}
data <- tibble(
  gene = readr::parse_factor(
    c(rep("miR34a asRNA", 5), rep("lnc34a", 3), "miR34a asRNA F1", "miR34a asRNA F10"),
    levels = c("miR34a asRNA", "lnc34a", "miR34a asRNA F1", "miR34a asRNA F10")
  ),
  feature = c(
    "exon", "intron", "exon", "intron", "exon",
    "exon", "intron", "exon",
    "primer", "primer"
  ),
  start = c(
    9181991, 9182316, 9183633, 9183807, 9191393,
    9181737, 9182295, 9196912,
    9182279, 9182223
    ),
  stop = c(
    9182316, 9183633, 9183807, 9191393, 9191686,
    9182295, 9196912, 9197043,
    9182301, 9182244
  )
)

p <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = filter(data, feature %in% c("exon") & gene == "miR34a asRNA"),
    aes(xmin = start, xmax = stop, y = gene, fill = gene),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    colour = "gray"
  )  +
  geom_segment(
    data = filter(data, feature == "intron" & gene == "miR34a asRNA"),
    aes(x = start, xend = stop, y = gene, yend = gene),
    linetype = "dotted",
    colour = "gray",
    size = 1
  ) +
  geom_segment(
    data = filter(data, feature == "primer"),
    aes(x = start, xend = stop, y = 1.1, yend = 1.1, colour = gene),
    size = 5 
  ) +
  labs(x = "Chromosome 1") +
  guides(fill = FALSE, colour = guide_legend(title = "Primer"))

plotRmarkdown(p) +
  theme_void() +
  scale_fill_brewer()
```

<div class = "caption">
3’-RACE schematic illustrating primer placement on the miR34a asRNA transcript for 3'-RACE.
</div>
